
\documentclass[
	a4paper, % Uncomment for A4 paper size (default is US letter)
	10pt, % Default font size, can use 10pt, 11pt or 12pt
]{resume} % Use the resume class

\usepackage{ebgaramond} % Use the EB Garamond font
\usepackage{hyperref}

%------------------------------------------------

\name{Charmaine Guo} % Your name to appear at the top

% You can use the \address command up to 3 times for 3 different addresses or pieces of contact information
% Any new lines (\\) you use in the \address commands will be converted to symbols, so each address will appear as a single line.

\address{118 Concord Road \\ Wayland, MA 01778} % Main address

% \address{123 Pleasant Lane \\ City, State 12345} % A secondary address (optional)

\address{(407)~$\cdot$~820~$\cdot$~7755 \\ charmaineguo06@gmail.com} % Contact information

\address{\textbf{Website:} \href{https://charmaineguo.com}{charmaineguo.com}}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
	
	\textbf{Northwestern University} \hfill \textit{June 2028} \\ 
	B.S. in Materials Science \& Engineering \\
	% Minor in Linguistics \smallskip \\
	Overall GPA: 3.031
	
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

	\begin{rSubsection}{Northwestern University}{October 2024 - Present}{Research Aide}{Evanston, IL}
		\item Collaborating with a graduate student on cellulose crystallization research, focusing on color formation without dyes.
		\item Studying how UV light cures acrylic acid, solidifying cellulose crystals and creating structural colors
		\item Analyzing using MATLAB how varying cellulose concentrations affect crystal arrangements and resulting colors.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Northwestern University}{Octor 2024 - Present}{Swim Instructor}{Evanston, IL}
		\item Customizing instruction strategies based on knowledgeable evaluations of students' abilities.
		\item Maintaining participant progress by offering regular feedback and technique suggestions.
		\item Leading 5 swim classes per week for over 25 total participants.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Weston Department of Public Works}{June 2024 - August 2024}{Engineer Intern}{Weston, MA}
		\item Analyzed and documented water pipe materials and diameters from hand-drawn maps; entering data into a new management system with a focus on GIS application.
		\item Studied and maintained the town’s water distribution system, including public and private water lines and meters.
		\item Supported water treatment plant analysis and operations, gaining practical knowledge of water infrastructure.
	\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

	\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
		Computer Languages & Python, Java, MATLAB, HTML, CSS \\
		Soft Skills  & Project Management, Teamwork \\
		Labratory work & Research Design, Lab Safety, Capillary Rheometer, Centrifuge, Speedmixer, ICP \\
		Organizational Tools & Microsoft Excel, Google Drive
		
	\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXTRACURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Extracurricular Activities}

    \begin{rSubsection}{Northwestern Formula SAE (NUFSAE)}{October 2024 -- Present}{Power Distribution Management}{}{}
    	\item Working on the electrical systems team to design the back box harness and build the top hoop harness.
    	        	\item Collaborating with the accumulator team to design the low voltage battery box.
        	\item Learning and applying software like Altium, SolidWorks, and RapidHarness.
        	\item Contributing to team milestones and ensuring technical goals align with deadlines.
    \end{rSubsection}

    \begin{rSubsection}{McCormick Student Advisory Board (MSAB)}{October 2024 -- Present}{Project Development Team}{}{}
        	\item Assisting in organizing departmental events to connect students with faculty and industry professionals.
        	\item Providing input on academic initiatives and fostering a collaborative environment for Northwestern McCormick School of Engineering  students.
    \end{rSubsection}

    \begin{rSubsection}{Tikkun Olam Makers (TOM)}{October 2024 -- Present}{}{}
%         	\item Collaborate with a multidisciplinary team to design assistive technologies for individuals with disabilities.
        	\item Use engineering, design, and rapid prototyping skills to develop low-cost solutions to real-world challenges.
        	\item Participate in hackathon-style events to build functional prototypes and present outcomes to stakeholders.
    \end{rSubsection}

    \begin{rSubsection}{Northwestern Water Polo Club}{October 2024 -- Present}{}{}
        	\item Participating in weekly practices and team tournaments to develop teamwork and athletic skills.
        	\item Supporting recruitment efforts and organizing club activities to enhance team dynamics.
    \end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

	%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
